% This section includes some motivations behind the work, explicitly or implicitly highlights the research question , provides a high-level explanation of the solution, and describes the contributions.

% establish the context, background and/or importance of the topic
In the current global economy, the financial fraud has become a crucial issue especially for the trade sector. In recent times, the number of fraud cases have increased drastically which effected both financial institutions and their clients significantly. From a survey in 2020 on economic crime and fraud by Price Waterhouse Coopers, its been reported that more than 42 billion USD of financial losses happened in past 24 months~\cite{PwC.Crime.Survey}. On an average companies reportedly experienced 6 fraud cases during this period. Thirty five percent of fraud cases are marked as Customer fraud~\cite{PwC.Crime.Survey}.   

In current trend, more and more, companies outsource non-core activities to third party companies to reduce operational costs. But these third party-party business partners can be fraught with risk. One in five respondents from the PwC survey~\cite{PwC.Crime.Survey} cited vendors/suppliers as the source of their most disruptive external fraud. On the other hand, suppliers are also in high risk of fraud cases from their buyers. Due to this detecting suspicious companies (buyers and suppliers) plays an important role to reduce financial losses for the trade insurance companies and theirs customers.


% brief synopsis of the relevant literature
Fraud or extortion is a par of internal threats for any business. Manufacturers and service providers may face financial losses from fraudulent buyers. According to Association of Certified Fraud Examiners (ACFE), the definition of fraud is "the use of one\’s occupation for personal enrichment through the misuse or deliberate
misapplication of the resources or assets of the employing organization" \cite{kassem_2014}. To term fraud that is imposes to manufactures and service provider it can be redefined as the personal gain of the buyers by misuse or deliberate misapplication of the products and services of the supplying organization and their respective insurance companies.

% Indicate an issue, problem or controversy in the field of study

% listing the reasarch question or hypotheses

% provide synopsis of the research methols

% Significance of value of the study

% Define the topic or key term

% Overview of teh report stucture

% State the purpose of the essay / write

% Provide an overview of the coverage


Some estimates state that fraud costs US business more than \$400 billion annually

Data extracted is a useful method to gather data for analysing and prediction tasks. Data driven is a method base on the history data to build more hyper-parameters to compensate the un-measurable features within the measurable data \cite{SMARRA20181252}. some extending nonlinear features to build the prediction function. In classification and prediction problem, it is essential to discover the pattern of the data and provide us some insights to take some actions according to the prediction results. Random Forest algorithm has been used in handling this problem which are shown effective[4][5] and extensively used in many fields. However it is extremely hard to identify the target information from institutions data based on pattern. The propose of the paper is to find a suitable classifier and its application to find fraudulent cases. 

Random forest generally performs substantially well in cases like this over single tree classifier for imbalance dataset. The target of this paper is to use data-driven method and random forest algorithm in the classification problem to improve the prediction